\section{Design} \label{design}

	\subsection{Network and API Usage}

	Before the design can be considered, the expected use of the network must be examined. Although the network is for the storage of data, this data is not intended to be in the form of large files, rather, it is expected that services can use the network to store their state. A concrete example of such a service could be a ``social network'', where users can associate with each other, update their profile and make posts. Upon performing actions, the user would send an update to each user they associate with, which they would later receive and act on accordingly.

	Any service will desire a guarantee on availability, so this must be taken into account.

	The main aim of the protocol is to write the rules of internodal communication within the network. The protocol should therefore define how a node can connect to the network, discover other nodes, the process of transferring data between nodes and the logical topology of the data stored.

	The main goal of the network is to allow messages to be inserted and received later by the intended recipient. This should be done in a way that makes the message highly available.

	The API should provide an interface with the network, abstracting the details of the actual insertion/retrieval away.

	The general idea for the network is that the API will be able to take a message, apply some function to this and distribute it across the network to make it highly available, such that the function makes the message unreadable to anyone that is not a recipient. To retrieve a message for a particular user, all data in the network can have the inverse function applied to it to retrieve messages intended for them. This high-level abstraction is shown in \todo[inline]{Need to add sequence diagram}. In reality, this function is likely to be a form of asymmetric cryptography operating on the public key of the recipient and the inverse an operation of the recipient's private key.\todo{Move?}
	
	\subsection{Considered Elements for Designs}
		Several key elements of a storage network were identified and different design decisions based around these elements were considered. 
		
		\subsubsection{Network Connectivity}
			In order to join the network, a node must have some knowledge of where to find other nodes. This can be achieved either through the use of some central authority that holds a list of nodes, enabling anyone to acquire the knowledge to use the network, or each node can act as a part of a decentralised directory, where as long as one node can be connected to, the remaining participants of the network can be discovered.
			
			Neither solution is flawless: the central authority could reduce security by providing a more important class of node that could be seen as a target by an adversary, while the acquisition of the knowledge needed to connect to the initial node would have to occur out-of-band and any information from a decentralised directory may be subject to abuse.
			
			Although the initial connection node may seem to be much the same as the central authority, it could be possible to have several of these initial connection nodes, and as long as they are members of the network, this should be acceptable. This presents any application the freedom to use any node as an initial connection node.
			
			As the introduction of a central authority presents too much risk and lowers the amount of freedom compared to a distributed directory, the API should provide a mechanism to allow users of the API to set initial connection nodes in order to discover the rest of the network.
			
			Given the nature of anonymous services, such as Tor's hidden services, the initiator of a connection is aware of the destination network identifier (or, pseudoidentity), although the target has no knowledge of the initiators psuedoidentity. This has the result that connections can be considered unidirectional, although the transfer of data is bidirectional once the connection is established. In some cases, determining the pseudoidentity of the initator is desired and so this presents an interesting challenge. The initator could tell the target their pseudoidentity, which the target could either check in some way, or trust. Alternatively, as the pseudoidentity is likely to have asymmetric key backing, a digital signature could be appended to a message, proving the pseudoidentity of the initator. 
			
			\todo[inline]{Speak about the actual fake pseudoidentity attack}
			
			\input{internodal-connections}
			
			The protocol dictates how nodes interact with each other and what topology to use. In some existing networks, such as Freenet, nodes organise themselves into a ``small-world topology'', where all nodes can connect to each other with a small number of hops. This is done in an attempt to keep nodes anonymous, but creates an attack vector where an adversary may be able to manipulate the topology to allow for attacks.
			
			A central authority to dictate the topology could be used, but introduces a point of failure, which should be avoided.
			
			As an existing anonymity layer will be used, there is no need to use the topology to keep nodes anonymous. Rather, it will be considered mainly for purpose of information distribution. 
			
			Since any topology that allows node connections to be directly manipulated presents a potential attack vector, a purely logical topology, where nodes each decide who they connect to unidirectionally should be used. Since this method relies on no external influence to any node, there is a chance that some nodes may not be selected for a connection by other nodes. While this is only an issue if a large number of nodes are not selected, as this effectively reduces the potential resources in the network, this number should be kept to a minimum. Formula \ref{eq:internodalconnections} shows the probability of any node not being selected by any other for a unidirectional connection. Figure \ref{fig:internodalconnections} shows this probability where each node maintains 20 unidirectional connections out. As shown, this probability is very low and even when the network is large, under the condition of periodic connection renewal so that newer nodes are included, it is likely that all nodes will always be connected by some other node.
			
			\todo[inline]{internodal connections}
		\subsubsection{Packet Classes}
			\begin{description}
				\item[Data as Notifications] \hfill \\
				A single class of data packet is used, where the intended message and notification of the existence of said message are combined. This means that if a notification is successful, the data will always be available, resulting in lower delivery latency. However, as the size of some packets could be large, and the majority of this information is destined for most nodes, this is likely to be wasteful and could cause scalability issues.
				\item[Notifications Referencing Data] \hfill \\
				2 classes of packet are used: a data packet that is just for storing data and a notification packet that is only for notifying a node about the existence of a data packet. While all nodes still need to check all the notifications, only a subset of all nodes need to be in possession of the data packets. In addition, the notifications may also include information such as some known locations of the desired data packet. This method has the potential to reduce the availability of data packets that are not distributed well throughout the network.
				\item[Notifications With Small Payload] \hfill \\
				Similarly to having notifications referencing data, notifications may also hold small amounts of data on the condition that the length is comparable to that of a typical notification packet. This results in having small amounts of data having very high availability, while larger data packets not causing scalability issues.
			\end{description}
			
		\todo[inline]{Have descriptions of the methods in this section and move the advantages/disadvantes out here?}
			
			Given that notifications with small payloads have the potential to provide maximal flexibility while also reducing the load on the network, these will be used.
			
		\subsubsection{Information Distribution and Delivery}
			Distributing the information across the network must occur in order to keep the availability of information high. In order to receive a message, everyone must either check every message, or there must be some form of delegation to a third party, or parties, that must check perform the same role.
			
			Systems, such as Bitmessage, take the approach that everyone can attempt to determine if a message is for them, whereas other systems, such as email, take advantage that the recipient of a message can be determined and use this place the message in a predictable location. Other networks, such as Freenet, move the obligation of notification to out-of-band communications, meaning they do not address this issue.
			
			As the Bitmessage network grows, it splits into ``streams''~\cite{bitmsg}, effectively creating smaller disjoint networks. Membership of a stream can be a function of some identifying element of the user, such as a public key (figure \ref{fig:stream-normal}). Although this method is promising in terms of scalability, it has some disadvantages for the anonymity of the network. This type of optimisation is only possible where each stream has enough members such that if the stream was isolated, the property of anonymity would hold. Under the assumption that there is a partial injection from users to nodes, it is enough for the node membership under any stream for be sufficiently high. However, if this assumption cannot be made, then it opens the possibility to deanonymisation attacks. The worst-case for this attack is that it may be possible to determine the public key, and therefore the identity that a node is interested in retrieving messages for. This would occur where an adversary is able to isolate a node in a stream (figure \ref{fig:stream-malicious}). This could happen where an adversary creates a large number of nodes with similar public keys (through trial and error, or otherwise) to the target node. Although this may only reveal the recipient's identity for new packets in the stream where the isolation attack is taking place, it is still undesirable.
			
			\input{streams-1}
			
			While all nodes need to check all messages to a degree, this mechanism is only required to notify of a message. Hence, instead of combining the notification and data functionality in a single packet, and having everyone acquire all of these, a split can be made. This would still require everyone to acquire and check all the notification packets, but these notifications could point to a data packet elsewhere on the network, along with a collection of nodes that are known to be in possession of these data packets.
			
		\subsubsection{Broadcast Handling}
			Notifications will be broadcast to at least all nodes that are members of a stream, this is likely to be the bottleneck of the system. The handling of broadcasts should therefore be subject to optimisation where possible.
			
			\begin{description}
				\item[Universal Polling (UP)] \hfill \\
				Nodes query other nodes for a list of their stored broadcasts, likely in the form of a distributed hash table. The querying node then can then request any broadcast it does not have stored. If the rate of broadcasts inserted into the network is greater than the rate they expire, then the size of the query response will grow in an unsustainable way.
				\item[Active Forwarding (AF)] \hfill \\
				Upon receiving a broadcast, the node forwards it onto all of its connections. This does not require any list of broadcasts to be distributed, saving on some overhead. However, as the node initiating the forwarding is unaware if the nodes are in possession of the broadcast, the receiving node will be responsible for signalling that further transfer is not required, probably in the form of terminating the connection.
				\item[Selective Polling (SP)] \hfill \\
				When a node receives a broadcast, it also stores the time of receipt. When a node performs a poll on another node, it stores the time of polling for that node. In a similar way to UP, polling is used to gather a list of broadcasts, but a parameter specifying the last time of polling is passed too. The polled node returns the list of all broadcasts that it received after this time. This has potential anonymity implications where it may reveal the time at which a node received a broadcast. However, this can be negated by having the receiving node add a small random time to the real time of receipt.
			\end{description}
			\input{broadcast-handling-scatter}
			Simulations for each of the 3 broadcast handling methods were run for a set period of time. For the interval up to this time, nodes are stimulated, adding nodes for them to perform, such as querying another node or pushing data into the network. After the allowed simulation time, no more stimulations occur and the remaining tasks are allowed to complete. The interval from stopping stimulations to the end of the simulation is referred to as the simulation lag. More detail on the simulator can be found in \ref{simulator}. \todo{Add ref} It should be noted that time, in this context, is measured in simulation ticks, not the real time the simulation takes to complete. Small simulation lag values are what is expected to result from a sustainable system where tasks do not accumulate.
			
			Simulation results are not absolute, and real scalability and performance results will be dependant on real network usage. The simulations presented here, subject to minor variation in the random nature of ``simulating'' usage, have been conducted under the same usage conditions.
			
			Running the simulation for UP for a set time, while varying the size of the network results in the graph shown in figure \ref{fig:simulation-lag}. The point where the method fails for a simulation interval of $150\cdot10^6$ ticks, can be seen to occur at 80 nodes. For UP, the points of failure for different simulation times were plotted, as shown in figure \ref{fig:critical-point}. This downward trend indicates that the number of nodes needed to create network failure decreases the longer the network is active.
			
			Simulations for SP and AF were also conducted, but points of failure could not be determined.
			
			The simulations were run for $300\cdot10^6$ ticks, to achieve near steady-state behaviour in the network. 
			The bandwidth used over each of the simulations was compared, as shown in figure \ref{fig:bandwidth-required}.
			
			SP has the potential to require the least bandwidth for broadcasts. AF may also be useful to support for the purpose of initial packet distribution, to both increase availability faster and to increase anonymity by hiding the original source of packets.
			
	\subsection{API}
		The primary objective of the system is to provide an API that allows for sending and receiving of messages. The node implementation and protocol are therefore designed around this objective.
		
		The API is designed to revolve around 2 functions: send and receive. Sending requires knowledge of the public identity of the sender, the message and how long it should be stored in the network. Receiving requires knowledge of a private identity, which returns a message for the given identity. Both functions are blocking, meaning that sending will block until the message is in the network and receiving will block until a message that has not been received previously is returned. Figure \ref{fig:api-uml-design} shows the general design for the API.
	\subsection{Abstract Protocol}
	
	\subsection{Node Implementation}
	
	\subsection{Final Design}
		\subsubsection{Node Implementation}
		
			\todo[inline]{This is set in the future tense. Bring it into the present?}
		
			The node is designed to be the component of the network that will handle implementation of the protocol used to communicate with other nodes. The API will also interface with the node in order to facilitate insertion and retrieval from the network.
			
			Nodal communications are intended to support a RESTful interface using HTTP for transfers. Each addressable node has the following URLs:
				\todo{Check}
				/info - A GET request will result in a representation of the node's information including the proof of work algorithms that are accepted and what difficulty is required for them.
				/data - 
				
			Communications will require the serialisation of some data structures to pass them between nodes. Rather than force a single technique for all nodes, multiple serialisation methods can be supported by using a HTTP \textit{Accept} header to express preference. A HTTP \textit{Unacceptable} error message can be set if there is no common serialisation method between the 2 communicating nodes.
			
			A database will be used to provide persistence across executions. Activity observations will be kept in an attempt to determine which nodes are likely to be active on startup, giving quick access to the network. Records of when nodes were last polled will also be stored to prevent wasting bandwidth. Any packets held will also persist to increase availability.
			
			Connections between nodes will be handled by a connection module. Nodes can be thought of as in 4 categories: \emph{active}, where it is known to be online; \emph{inactive}, where it is known to be offline; \emph{unknown}, where there is some uncertainty as to the node's status and \emph{undiscovered}, where the node is not known about at all. Initially, when a new node is created, all nodes can be considered undiscovered with the exception of any initial nodes, which are tested and if online, classed as active and queried for their lists of nodes, while also being informed about the new node's address, allowing other nodes to later find it. The status of any newly discovered nodes is treated as unknown until a connection is established, where their activity can be determined. 
			
			Each node should attempt to keep a list of 20 active nodes, which will be used for unidirectional anonymous communications. This list should be renewed periodically both to increase anonymity and to utilise newer nodes.
			
			To determine which packets are stored on other nodes, selective polling will be used to enumerate packets and their class that a node first received after a certain time. This information will then be stored in the database. All broadcast packets should be retrieved. Data packets may be retrieved
			
			
			
			Proof of work is required to deter abuse within the system. A proof of work consists of a proof of work algorithm (along with the difficulty parameters); the period of time the data is valid for; a checksum of the data; and a generated nonce.
			
			Each node has a collection of acceptable proof of work algorithms along with the relevant difficulty parameters. These difficulty parameters are likely to consist of a constant and a coefficient term, allowing the difficulty to be computed by \ref{eq:difficulty}. 
			
			\begin{equation} \label{eq:difficulty}
				\text{difficulty} = \text{constant} + \text{size} \times \text{period} \times \text{coefficient}
			\end{equation}
			
			Proof of work algorithms, such as that described in Hashcash use an exponential approach in order to acheieve difficulty. In Hashcash, the difficulty is equal to the number of nybles at the start of the proof of work checksum that are zero, and hence, the amount of work required is an exponential function of the difficulty. This exponential nature is well-suited for systems that only require a change of difficulty in the long term. For Stor, although not a requirement for proof of work algorithms, ideally the amount of work should scale linearly to the difficulty. To achieve this, the difficulty is first transformed onto a finite number line with equation \ref{eq:transdif}. The proof of work is valid if the relevant hash is less than or equal to this transformed difficulty.
			
			\todo[inline]{Mention included POW (and hashes)}
			
			\begin{equation} \label{eq:transdif}
				\text{difficulty}' = \underbracket{M}_\text{maximum} - \frac{\text{difficulty}}{M}
			\end{equation}
			
			\begin{equation}
				\text{Hash}(checksum, period, size, nonce) \le \text{difficulty}'
			\end{equation}
			
			\input{pow}
			
			\todo[inline]{Use cases?}
			
		\subsubsection{Protocol}
			
			\input{protocol.tex}
			
			