%Test Plan
\begin{landscape}
	\section{Test Plan} \label{testplan}
	
	\renewcommand{\arraystretch}{1.2}
	
	\subsection{Unit Tests}
		\label{sec:unit-tests}
	\begin{table}[!htbp]
		\begin{tabular}{| l | p{13cm} | l |}
			\hline
			Unit Test & Description & Pass/Fail \\ \hline
			
			\texttt{testGeneration} & Tests that a valid proof-of-work is generated so that it would be accepted. & Pass \\ \hline
			\texttt{testFakeValidity} & A fake proof-of-work validity period is tested to ensure that it is not accepted. & Pass \\ \hline
			\texttt{testFakeData} & A fake proof-of-work packet hash is tested to ensure that it is not accepted. & Pass \\ \hline
			\texttt{testFakeProof} & Tests a fake proof-of-work nonce to ensure that it is not accepted. & Pass \\ \hline
			\texttt{testCheckForMe} & Tests the method that checks for packet receipt on a packet that is for a held identity & Pass \\ \hline
			\texttt{testCreationFromBase64} & Checks that identities can be created from a Base64 string & Pass \\ \hline
			\texttt{testSuccessfulDecryption} & A packet is encrypted and decrypted, checking that the message is unchanged & Pass \\ \hline
			\texttt{testCheckNotForMe} & Tests the method that checks for packet receipt on a packet that is not for a held identity & Pass \\ \hline
			\texttt{testBroadcastGeneration} & Tests the protobuf for the serialisation/deserialisation of broadcasts & Pass \\ \hline
			\texttt{testInformation} & Tests the JSON serialisation/deserialisation of nodal information & Pass \\ \hline
			\texttt{testNodeDiscoveryInformation} & Tests the serialisation/deserialisation of the internodal communications for exchanging node discovery information & Pass \\ \hline
			\texttt{testParams} & Tests the serialisation/deserialisation for exchanging proof-of-work parameters & Pass \\ \hline
		\end{tabular}
	\end{table}
	
	\newpage
	\subsection{Manual Usability Tests}
		\label{sec:usability-tests}
	\begin{longtable}{| l | p{7cm} | p{7cm} | p{5cm} | l |}
			\hline
			ID & Description & Expected Result & Possible Failures & Pass/Fail \\ \hline
			\endhead
			0 & Node reports failure if unable to connect to a local tor control connection. & Stor throws an exception, mentioning that a connection could not be made and explaining how to fix it. & Case not checked. \newline Exception not thrown. & Pass \\ \hline
			
			1 & New node creates a hidden service & Stor finds no existing hidden service and creates one using the control connection. Can be tested by establishing a connection to the hidden service through Tor. & Failure to detect no existing hidden service exists. \newline Hidden service is not created. & Pass \\ \hline
			
			2 & Read configuration and use parameters & Stor uses the configuration file to establish a secure control connection to the local tor instance. & Does not read config. \newline Does not use values in config. & Pass \\ \hline
			
			3 & Web interface accessible & Requests are made through the locally bound interface and through the hidden service interface. Responses are expected on both. & Does not bind to an interface.\newline Request not handled. & Pass \\ \hline
			
			4 & Valid selective polling response & Packet is given to the node at a known time $t$ and polling requests made before/after this time to ensure the packet does not appear for a request before $t$, but appears for requests after $t$. & List of packets is not as expected. & Pass \\ \hline

			5 & Node accepts (POST) forwarded data & Some data is forwarded to the node to check acceptance. & Request not handled & Pass \\ \hline
			
			6 & Node accepts forwarded packet & Node made to forward packet to self. & Packet forwarding/receipt not handled correctly. & Pass \\ \hline
			
			7 &
			Node accepts only valid packets &
			Invalid packets (invalid PoW, expiry, malformed) are forwarded to the node and not stored. &
			Node stores invalid packet &
			Pass \\ \hline
			
			8 &
			Node handles malformed requests gracefully &
			Malformed serialised forms are sent to the node and a bad request error code returned. &
			Node throws exception and crashes &
			Pass \\ \hline
			
			9 &
			Information response &
			Node is queried about its accepted proof-of-work algorithms and responds with a list. &
			Request not handled &
			Pass \\ \hline
			
			10 &
			Node discovery &
			A node with some knowledge of other active nodes is queried and the list of these nodes is given. &
			Request not handled \newline Missing nodes &
			Pass \\ \hline
			
			11 &
			Key zeroisation &
			Hooks are used to clear any keys from memory upon shutdown or instance finalisation. &
			Hooks not fired \newline Keys not cleared &
			Fail \\ \hline
		
			12 &
			Nodes blacklisted after malicious behaviour &
			Nodes not following the protocol are blacklisted. &
			Not implemented &
			Fail \\ \hline

			13 &
			API sends &
			The send function inserts a message into the network. &
			Message not inserted &
			Pass \\ \hline

			14 &
			API receives &
			The receive function gets a message for a given identity. &
			Hook into live packet feed fail \newline Message not received &
			Pass \\ \hline

			15 &
			.onion addresses resolved locally &
			Hidden service addresses are resolved locally only. &
			Resolution is passed through to normal DNS servers &
			Pass \\ \hline
			
			16 &
			Rejection of misclassified packets &
			A packet with the wrong class flag is not accepted. &
			Class flag is not used as a measure of validity &
			Pass \\ \hline
			
			17 &
			Time zones not leaked &
			All time zones used should be GMT only, even on foreign systems. &
			Non-GMT time zones are used &
			Pass \\ \hline
	\end{longtable}
\end{landscape}